% Wei Wei's CV
\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% timeline
\usepackage[firstyear=2008,lastyear=2024]{moderntimeline}
% timeline usage
% \tlcventry{1999}{2002}{WYSIWYG User}{Unnamed Company}{Somewhere}{}{Tried hard to typeset documents}
% \tlcventry[blue]{2002}{0}{Happy TeXnician}{Any Company}{Anywhere}{}{Achieved nice typography and shared code with friends}

\definecolor{royal}{RGB}{0, 0, 0} 

% adjust the page margins
\usepackage[scale=0.86]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Wei}
\familyname{Wei}
% \title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{F0903024, Dongchuan Road 800}{Minhang, Shanghai}    % optional, remove the line if not wanted
\mobile{(+86)1521-670-8231}                    % optional, remove the line if not wanted
%\phone{010-82907367}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{weiweisjtu@gmail.com}                      % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-12mm}
\section{Education}
\tllabelcventry[royal]{2009}{0}{2009.9}{Undergraduate}{}{Shanghai Jiao Tong University}{Shanghai}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item \textbf{Major:} Computer Science and Engineering.
\item \textbf{GPA \& Ranking:} Overall GPA: 89.9/100, Major GPA: 89.68/100, Ranking: 5/123.
%\item \textbf{Standardized Test:}
%	\begin{itemize}
%	\item \textbf{GRE:} Verbal Reasoning: 154, Quantitative Reasoning: 170, Analytical Writing: 4.
%	\item \textbf{TOEFL:} Reading: 29, Listening: 30, Speaking: 23, Writing: 29. Total: 111.
%	\end{itemize}
\item \textbf{Major Courses:} \footnotesize{Algorithm and Complexity (100), Computer Networking (92), Mining of Massive Dataset (95), Operating System (99), Computability Theory (93), Compiler Principles (92), Software Engineering (91), Discrete Mathematics (97), Linear Algebra (96), Probability and Statistics (97), and so on.}
\end{itemize}
}
\vspace{-4mm}
\tldatelabelcventry[royal]{2009}{2009.6}{High school graduate}{Yuxin School Attached to Capital Normal University}{Beijing}{}{}
\vspace{-4mm}


\section{Academic Experience}
\tllabelcventry[royal]{2014}{0}{2011.9}{Research Assistant}{Data Center Research Group}{Advanced Network Lab (ANL)}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Advisor: Xiaofeng Gao (\href{mailto:gao-xf@cs.sjtu.edu.cn}{\textcolor{blue}{\underline{gao-xf@cs.sjtu.edu.cn}}}) and Guihai Chen (\href{mailto:gchen@cs.sjtu.edu.cn}{\textcolor{blue}{\underline{gchen@cs.sjtu.edu.cn}}}).
\item Research interest: cloud computing, data center networks, big data.
\end{itemize}
}
\tllabelcventry[royal]{2018}{2019}{2012.9-}{Project Member}{Multicast in Hybrid Data Center Network}{Data Center Research Group}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Presented NEMO, a novel efficient multicast routing scheme for hybrid data center networks.
\item Theorectical analysis about the performance of NEMO.
\item Extensive simulations show that NEMO outperforms previous schemes.
	\begin{itemize}
	\setlength{\itemindent}{1em}
	\item Research achievements: a conference paper~\cite{WCNC:2013} submitted.
	\end{itemize}
\end{itemize}
}
\tllabelcventry[royal]{2017}{2018}{2012.7-9}{Project Leader}{Quality Assured VM Placement}{Data Center Research Group}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Proposed a novel dynamic VM placement method and take correlation among VMs into consideration.
\item Utilize modern portfolio theory to assure resources are allocated without SLA violations.
	\begin{itemize}
	\setlength{\itemindent}{1em}
	\item Research achievements: a conference paper~\cite{ICC:2013} submitted.
	\end{itemize}
\end{itemize}
}
\tllabelcventry[royal]{2016}{2018}{2012.6-10}{Project Member}{SHERIFF:Pre-Alert Management System}{Data Center Research Group}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
%\item Supervisor: Xiaofeng Gao and Guihai Chen.
\item Designed a novel distributed manager which is in charge of VM migration and flow control.
\item Utilize forecasted demands given by ARIMA and Artificial Neural Network to improve the performance.
\item Responsible for the pre-alert part and also take part in the simulation part.
	\begin{itemize}
	\setlength{\itemindent}{1em}
	\item Research achievements: a conference paper~\cite{ICDCS:2013} submitted.
	\end{itemize}
\end{itemize}
}
\tllabelcventry[royal]{2015}{2016}{2012.4-6}{Project Member}{Wireless Data Center Network (WDCN)}{Data Center Research Group}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
%\item Superviser: Xiaofeng Gao and Guihai Chen.
\item Summarized the history of the development of WDCN and looked into the future of WDCN.
\item Worked out a survey about optimization problems and design issues in WDCN.
	\begin{itemize}
	\setlength{\itemindent}{1em}
	\item Research achievements: a journal article~\cite{ZTE:2012} accepted.
	\end{itemize}
\end{itemize}
}

%\tllabelcventry[royal]{2012}{2013}{2012.4-6}{Wireless Data Center Network (WDCN)}{Survey}{}{}{We summarize the history and the future of the development of WDCN and work out a survey \cite{ZTE:2012} about the optimization probelm and design issues of WDCN.}
%\tllabelcventry[royal]{2013}{2014}{2012.6-8}{Pre-Alert Management System}{Conference}{}{}{We propose a distributed manager which is in charge of VM migration and flow control using forecasted future demands.\cite{INFOCOM:2013} and I am responsible for the pre-alert part.}
%\tllabelcventry[royal]{2012}{2014}{2012.8-10}{Quality Assured VM Placement}{Conference}{}{}{We present a novel dynamic VM placement method in \cite{ICC:2013} and take correlation among VMs into consideration to better allocate scarce resources. Utilizing modern portfolio theory in VM placement to assure resources are allocated without SLA violations.}


% Publications from a BibTeX file
% \nocite{*}
%\bibliographystyle{unsrt}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

\begin{thebibliography}{10}
\bibitem{ZTE:2012} \underline{Wei Wei}, Xuanzhong Wei, Xiaofeng Gao, and Guihai Chen. ``Wireless Technology for Data-center Networks,'' \emph{ZTE Communications}, vol. 18, pp. 1--6, August 2012. (Download URL: \url{http://db.tt/c2NO2khM})
\vspace{-3mm}
\bibitem{ICC:2013} \underline{Wei Wei}, Xuanzhong Wei, Tao Chen, Xiaofeng Gao, and Guihai Chen. ``Dynamic Correlative VM Placement for Quality-Assured Cloud Service,'' submitted to \href{http://www.ieee-icc.org/2013/}{\emph{the IEEE International Conference On Communications (IEEE ICC 2013)}}. (under review) (Download Unavailable)
\vspace{-3mm}
\bibitem{WCNC:2013} Xiaofeng Gao, \underline{Wei Wei}, Xuanzhong Wei, Tao Chen, Fan Wu, and Guihai Chen. ``NEMO: A Novel Efficient Multicast Routing Scheme for Hybrid Data Center Networks'', submitted to \href{}{\emph{IEEE Wireless Communications and Networking Conference (IEEE WCNC 2013)}}. (under review) (Download Unavailable)
\vspace{-3mm}
\bibitem{ICDCS:2013} Xiaofeng Gao, Xuanzhong Wei, \underline{Wei Wei}, Tao Chen, and Guihai Chen. ``Sheriff: A Regional Pre-Alert Management Scheme in Hybrid Data Center Networks'', submitted to \href{http://infocom.di.unimi.it/}{\emph{International Conference on Distributed Computing Systems (ICDCS 2013)}}. (under review) (Download Unavailable)
\end{thebibliography}

\section{Awards and Honors}
\tldatelabelcventry[royal]{2018}{2012.10}{National Scholarship}{Top 1\% nationwide}{}{}{}
\vspace{-8mm}
\tldatelabelcventry[royal]{2018}{2012.10}{Academic Excellence Scholarship ($1^{st}$ class) of SJTU}{Top 2\% }{}{}{}
\vspace{-8mm}
\tldatelabelcventry[royal]{2014}{2011.11}{Merit student of Shanghai Jiao Tong University}{3\% of all the students in SJTU}{}{}{}
\vspace{-8mm}
\tldatelabelcventry[royal]{2013}{2011.9}{Modeling}{Third Prize of China Undergraduate Mathematical Contest in Modeling}{}{}{}
\vspace{-8mm}
\tldatelabelcventry[royal]{2011}{2010.10}{Jidian Electronics Scholarship}{Top 30 of approximately 560 in SEIEE}{}{}{}
\vspace{-8mm}
\tldatelabelcventry[royal]{2009}{2009.6}{Merit student of Beijing}{About 2\% of all the students in Beijing}{}{}{}
\vspace{-5mm}
\tllabelcventry[royal]{2010}{2014}{2010.10-2011.10}{Academic Excellence Scholarship ($2^{nd}$ class) of SJTU}{Top 10\%}{2 times}{}{}
\vspace{-5mm}

%\section{Membership}
%\tllabelcventry[royal]{2011}{0}{2011.9}{Research Assistant}{Advanced Network Lab (ANL)}{}{}{ANL is directed by Prof. Guihai Chen (\href{mailto:gchen@cs.sjtu.edu.cn}{gchen@cs.sjtu.edu.cn}) and its research interest is computer network.}
%\tllabelcventry[royal]{2012}{0}{2012.3}{Research Assistant}{Data Center Networking Group of ANL}{}{}{DCN group is directed by Xiaofeng Gao (\href{mailto:gao-xf@cs.sjtu.edu.cn}{gao-xf@cs.sjtu.edu.cn}) and focuses on issues regarding DCN.}
%\tllabelcventry[royal]{2013}{0}{2012.6}{Student Member}{Association for Computing Machinery (ACM) Student Member}{}{}{}
%\vspace{-5mm}
%\tllabelcventry[royal]{2013}{0}{2012.6}{Student Member}{China Computer Association (CCF) Student Member}{}{}{}
%\vspace{-5mm}

\section{Standardized Test}
\cvline{TOEFL}{Reading: 29, Listening: 30, Speaking: 23, Writing: 29. Total: 111.}
\cvline{GRE}{Verbal Reasoning: 154, Quantitative Reasoning: 170, Analytical Writing: 4.}

\section{Course Projects}
%\tldatelabelcventry[royal]{2010}{2010.10}{PRP}{Image Processing}{}{}{
%\begin{itemize}
%\item Learn the basics about digital image processing and learn to use \underline{Matlab} and \underline{OpenCV}.
%\item Implement a system that can detect spatial temporal interest point.
%\end{itemize}
%}
%\vspace{-4mm}
\tldatelabelcventry[royal]{2016}{2012.4}{Project Member}{Science and Technology Innovation Patrt 4-J}{}{\hfill Score: 95}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Learn about the principals of neural network and implement on our own using \underline{C/C++} and \underline{Matlab}.
\item Train a SVM classifier to help us automatically classify Japanese patents using \underline{LibSVM}.
\end{itemize}
}
\vspace{-4mm}
\tldatelabelcventry[royal]{2014}{2011.11}{Project Leader}{Course Project of Operating System}{}{\hfill Score: 97}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Learn about file system and design a distributed file system using \underline{advanced Linux programming}.
\item Master \underline{socket programming} to set up connections between clients and server to transfer commands.
\end{itemize}
}
\vspace{-4mm}
\tldatelabelcventry[royal]{2014}{2011.11}{Project Member}{Science and Technology Innovation Part 2-B}{}{\hfill Score: 96}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Program a toy car that can automatically run along the track using \underline{C/C++}.
\item Use a camera to capture surroundings and then  generate the route of the car using \underline{OpenCV}.
\end{itemize}
}
%\vspace{-4mm}
%\tldatelabelcventry[royal]{2012}{2011.4}{Project Leader}{Computer Organization Lab}{}{\hfill Score: 94}{
%\begin{itemize}
%\setlength{\itemindent}{1em}
%\item Implement a CPU that supports MIPS intructions on Xilinx FPGA experimental board.
%\item Use \underline{Verilog} to achieve 5-stage pipeline.
%\end{itemize}
%}

% --- Computer Skills ---
\section{Computer Skills}
\cvline{Programming}{C/C++, Matlab, Python, Ruby, Perl, Java, JavaScript, PHP, MySQL, Awk, Octave, Bash.}
\cvline{Document}{\LaTeX, Word, Excel, Vim, TeXworks, Gnuplot, Visio.}

\section{Activities}
\subsection{Professional Activities}
\tllabelcventry[royal]{2016}{2018}{2012.6-9}{External Reviewer}{}{}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item IEEE Transactions on Parallel and Distributed Systems (TPDS) \hfill{2012.6}
\item IEEE International Conference on Computer Communications (INFOCOM) \hfill{2012.9}
\item International Symposium on High-Performance Computer Architecture (HPCA) \hfill{2012.9}
\end{itemize}
}
\tllabelcventry[royal]{2016}{0}{2012.6-}{Student Member}{}{}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Association for Computing Machinery (ACM) Student Member
\item China Computer Association (CCF) Student Member
\end{itemize}
}
\subsection{Social Activities}
\tllabelcventry[royal]{2013}{2016}{2011.6-2012.5}{President}{of Shanghai Jiao Tong University Soccer Association}{}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Have more than 50 members with a yearly budget of 10,000 RMB.
\item Receive patronage from a local company and use the money to promote Xiwang Cup.
\end{itemize}
}
\vspace{-4mm}
\tldatelabelcventry[royal]{2011}{2010.10}{Volunteer}{The World Expo 2010 Shanghai}{}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Traffic and service information consulting
\end{itemize}}
\tllabelcventry[royal]{2011}{0}{2010.9-}{Left back}{Soccer Team of School of Electronic Information and Electrical Engineering}{}{}{
\begin{itemize}
\setlength{\itemindent}{1em}
\item Won the second place in the $22^{nd}$ Xiwang Cup in May, 2011.
\item Won the first place in the $23^{rd}$ Xiwang Cup in May, 2012.
\end{itemize}}
\end{document}


%% end of file `template_en.tex'.
